Your Paper Title

### 2025-04-02 paper/paper.qmd
updated first draft of implication, future research direction, and limitation

## Implications of Findings

## Limitations

@@

## Future Research Directions

>>>>

## Implications of Findings
Our statistical analysis reveals a significant inverse relationship between pre-flowering March temperatures and sakura bloom dates, with higher temperatures consistently associated with earlier flowering time. This temperature-dependent pattern aligns with the documented global warming trend observed over recent centuries, particularly the accelerated temperature increase in the modern era.

The predictive models generated through our research demonstrate robust statistical evidence that the progressive elevation of mean March temperatures, driven by global warming, will likely continue to advance cherry blossom flowering dates in coming decades. This phenological shift carries significant ecological, cultural, and economic implications. The alteration of these biorhythms may disrupt established ecological synchronizations between cherry trees and their pollinators, potentially affecting ecosystem functionality and biodiversity dynamics.

From a cultural perspective, the temporal shift in cherry blossom seasons need adjustments to traditional hanami celebrations and tourism schedules, which have historically been calibrated to conventional blooming periods. In addition, these modifications could impact cultural practices that have remained relatively consistent for centuries and negatively impact tourism economy that is built around it.

## Limitations
We would like to address several methodological limiting factors. Firstly, our analysis relies predominantly on data from Kyoto, representing a geographically limited subset that may not comprehensively reflect sakura phenological patterns across Japan's diverse climate regions. Secondly, although we used a merged dataset spanning from 800 CE to 2019, there are significant data gaps/missing values where we have to drop during the cleaning & merging of the two dataset. In addition, a notable limitation is the historical dataset's reliability, as large portions comprise of reconstructed values derived from local linear regression models or originated from primary sources that lack rigorous academic verification protocols. This presents challenges for establishing data provenance and reliability in accordance with contemporary scientific standards. Lastly, while our findings highlight temperature as a statistically significant predictor of bloom timing, the single-variable approach inherently overlooks other potential ecological factors. Variables such as precipitation patterns, photoperiod fluctuations, soil conditions, and winter chilling requirements may also contribute significantly to the observed advancement in flowering dates. A more comprehensive multivariate model would potentially yield enhanced predictive capacity and ecological insights.

@@

## Future Research Directions
For future research, we would like to establish regression tree models to enhance predictive capabilities regarding sakura phenological patterns. Unlike traditional linear models, regression trees offer robust forecasting mechanisms that can better accommodate complex interactions between variables, prioritizing predictive accuracy over interpretive simplicity. Next, we recommend adding in additional environmental parameters beyond temperature. Variables warranting investigation including but not limited to precipitation frequency and intensity, atmospheric humidity gradients, soil composition metrics, photoperiod fluctuations, and cumulative chilling units during dormancy periods. Such multidimensional modeling would potentially explain a greater proportion of the observed variability in bloom timing and provide more nuanced insights into the complex biological mechanisms governing cherry blossom phenology. Lastly, future research could benefit from expanding the geographical scope beyond Kyoto to establish comparative phenological datasets across diverse microclimates and latitudinal gradients throughout Japan and other regions where cherry trees are important. This expanded spatial analysis would facilitate the identification of region-specific responses to climate variables and potentially isolate genetic adaptations to local environmental conditions.
